### 2017-10-27 pkg/model4you/inst/JORS/man_model4you.Rnw
typos
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1666 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 271e0965ae354d08d23e9ecb527d8f0be3fa30dd

The tree (see Figure~\ref{fig:math_tree}) divides students based on the
percentage of successful online \Sexpr{'tests'}. These online tests were
conducted biweekly throughout the semester.  The largest difference between the
two exam groups is in the students who did very well in the online tests (more
than \Sexpr{round(tr_math[[5]]$node$split$breaks, 1)} percent correct). The
tree thus gives us much more information on the fairness of the exam than the
simple linear model, which is that it does not seem to be fair for students who
did very well thrughout the semester (at this point we should state that the
students self selected into the two exam groups which might also be the reason
for differences in exam performance).

@@

Dependence plots with the group effect (treatment effect) on the y-achsis and
the student characteristics on the x-axis are a good way of visualising the
personalised models and for getting knowledge about the interactions between
student characteristics and the treatment. Since the percentage of successfull
online tests is measured on a grid, a bee plot possibly shows the relationships
even better than the scatter plot (both shown in Figure~\ref{fig:math_dp1}).
<<math_dp1, fig.width=4, fig.height=3, out.width='.48\\linewidth', fig.cap="Dependence plot for percentage of tests successfully solved.", fig.subcap=c("Scatter plot.", "Bee plot.")>>=
dpdat_math <- cbind(pmods_math, MathExam)

@@

\section*{Implementation and architecture}
The R package \emph{model4you} is focussed on ease of use and interpretability.
Users can take a simple model that they know and understand as basis and simply
plug it into \Sexpr{'pmtree()'} or \Sexpr{'pmforest()'} depending on whether
they want subgroup wise or personalised models. The basis for these
functionalities is provided by the \emph{partykit} package which is a widely
used R package for trees and forests. The \emph{model4you} package provides
wrappers for the well implemented and tested functions
\Sexpr{'partykit::ctree()'} and \Sexpr{'partykit::cforest()'} and extends the
functionalities to allow for the computation of personalised models and to 
improve usability and interpretability.

>>>>

The tree (see Figure~\ref{fig:math_tree}) divides students based on the
percentage of successful online \Sexpr{'tests'}. These online tests were
conducted biweekly throughout the semester.  The largest difference between the
two exam groups is in the students who did very well in the online tests (more
than \Sexpr{round(tr_math[[5]]$node$split$breaks, 1)} percent correct). The
tree thus gives us much more information on the fairness of the exam than the
simple linear model, which is that it does not seem to be fair for students who
did very well throughout the semester (at this point we should state that the
students self selected into the two exam groups which might also be the reason
for differences in exam performance).

@@

Dependence plots with the group effect (treatment effect) on the y-axsis and
the student characteristics on the x-axis are a good way of visualising the
personalised models and for getting knowledge about the interactions between
student characteristics and the treatment. Since the percentage of successfull
online tests is measured on a grid, a bee plot possibly shows the relationships
even better than the scatter plot (both shown in Figure~\ref{fig:math_dp1}).
<<math_dp1, fig.width=4, fig.height=3, out.width='.48\\linewidth', fig.cap="Dependence plot for percentage of tests successfully solved.", fig.subcap=c("Scatter plot.", "Bee plot.")>>=
dpdat_math <- cbind(pmods_math, MathExam)

@@

\section*{Implementation and architecture}
The R package \emph{model4you} is focused on ease of use and interpretability.
Users can take a simple model that they know and understand as basis and simply
plug it into \Sexpr{'pmtree()'} or \Sexpr{'pmforest()'} depending on whether
they want subgroup wise or personalised models. The basis for these
functionalities is provided by the \emph{partykit} package which is a widely
used R package for trees and forests. The \emph{model4you} package provides
wrappers for the well implemented and tested functions
\Sexpr{'partykit::ctree()'} and \Sexpr{'partykit::cforest()'} and extends the
functionalities to allow for the computation of personalised models and to 
improve usability and interpretability.
